Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-19 paper/main.tex
add AbstractProject description to all_projects bullet in sec 2.2.4

After importing Davos into a notebook, the top-level \texttt{davos} module exposes a set of attributes whose values determine various aspects of Davos's behavior. Most of these attributes are writeable options that can be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example and Sec.~\ref{subsec:implementation} for implementation details and additional information). These include:

@@

\begin{itemize}
\item \texttt{.active}: This attribute controls whether support for \texttt{smuggle}
  statements and onion comments is enabled (\texttt{True}) or
  disabled (\texttt{False}).  When Davos is first imported,
  \texttt{davos.active} is set to \texttt{True}.

@@

\item \texttt{.all\_projects}: This attribute contains a list of all Davos projects (as \texttt{Project} objects) that exist on the user's local system. See Section~\ref{subsec:projects} for more information about Davos projects.

>>>>

After importing Davos into a notebook, the top-level \texttt{davos} module exposes a set of attributes whose values determine various aspects of Davos's behavior. Most of these attributes are writeable options that can be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example). These include:

@@

\begin{itemize}
\item \texttt{.active}: This attribute controls whether support for \texttt{smuggle}
  statements and onion comments is enabled (\texttt{True}) or
  disabled (\texttt{False}).  When Davos is first imported,
  \texttt{davos.active} is set to \texttt{True} (see Sec.~\ref{subsec:implementation} for implementation details and additional information).

@@

\item \texttt{.all\_projects}: This attribute contains a list of all Davos projects that exist on the user's local system (see Sec.~\ref{subsec:projects} for more information about Davos projects). Each item in this list is either a \texttt{Project} or \texttt{AbstractProject} instance. \texttt{AbstractProject}s represent notebook-specific projects whose associated notebooks no longer exist. They support all the same functionality as \texttt{Project} objects (including methods for inspecting, renaming, and deleting them) and serve primarily to help users identify and clean up extraneous projects left behind after deleting Davos-enhanced notebooks (e.g., see Sec.~\ref{subsec:toplevel}).
\textcolor{red}{\textbf{TODO}: mention that project can become AbstractProject when notebook is moved/renamed, and can be re-linked by renaming project to new path?}
